Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
finished up experiment flow section

\noindent {\bfseries Experiment Flow} 
{\color {red}
% explain one experiment from start to end. 
At the start of the study, participants will be informed
of the role they they will be playing in the study. Particularly,
they will be informed that they are in a censorship environment
which prevents them from visiting certain websites, but they
are people who would like to visit those websites for 
leisurely purposes.

%talk about how participants will be motivated to configure to 
%complete these tasks. participants will write down the answers 
%on a sheet of paper...

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc. We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.} \\

>>>>

\noindent {\bfseries Experiment Flow} 
We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit a non-blocked website and a blocked website on a ``standard'' browser (one that is not used for censorship circumvention, such as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will be informed of the role they they will be playing in the study. Particularly,
they will be informed that they are a normal citizen in a censorship environment
which prevents them from visiting certain websites, that they are visiting the website for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given so that the participants can have an idea of the role they are playing, and to achieve consistency across participants. Their behavior might be different if they were visiting websites to accomplish a critical task, or if they knew that there were great risks.

After explaining the situation and their role, we will explain what Tor is, and how they can use it if necessary, and instruct them to complete the a set of tasks which will require visiting blocked websites. Ultimately, the participants will need to configure their Tor Browser to circumvent the simulated censorship environment. These tasks have a three-fold purpose of providing participants with feedback (if they did not correctly configure their browser, they cannot reach the website),  motivating the participants to configure the browser correctly, and providing the researchers with an indicator of successful censorship circumvention.

We will end the experiment with a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.  A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.\\
